CDSR Human Data/Modelling Paper

### 2013-08-08 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
Abstract Draft

\begin{abstract}
Abstract goes here
\end{abstract}

@@

\subsection{Kernel Methods - NICK}

>>>>

\begin{abstract}
Representing and reasoning about spatial terms is an essential ability for cognitive systems interacting with humans in a shared environment.  Consider a safe area in a military engagement.  The size, shape, and location of this area depend the the capabilities of the other agents and their capabilities in the environment.  We call these regions \textit{context-dependent spatial regions}(CDSRs).  We claim that understanding these regions requires integrating semantic and geometric knowledge about a dynamic environment.  We conducted a human study to explore how people interpret three types of CDSRs that supports the knowledge integration claim.  We evaluate two representation techniques against the human data and discuss their limitations as a cognitive systems solution to this problem.
\end{abstract}

@@

\subsection{Spatial Function Method - NICK}
